Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-24 tsibbletalk.Rmd
done proofing and checking

Close to the heart of the \CRANpkg{tsibbletalk} package is blending the best bits from \CRANpkg{tsibble}, \CRANpkg{crosstalk}, \CRANpkg{plotly}, and \CRANpkg{shiny}.

The `as_shared_tsibble()` turns a `tsibble` object to a shared data class, with an option to express any nesting and crossing structures from the `key` attribute. If nesting is found in the data, the `plotly_key_tree()` creates an interactive hierarchical tree to help with data overview. This sets the stage for hierarchical and categorical linking between multi-views from one shared tsibble.

A new shiny module, `tsibbleWrapUI()` and `tsibbleWrapServer()`, provides a lens for looking at temporal aspects for a `tsibble`, in particular seasonal or cyclical variations. The slicing and dicing technique efficiently wrap time lines for user-defined plots. The `plotlyProxy()` react method makes it possible to send wrapped data to the server and amend the plot straight way.

>>>>

At the heart of the \CRANpkg{tsibbletalk} package is a blending the best bits from \CRANpkg{tsibble}, \CRANpkg{crosstalk}, \CRANpkg{plotly}, and \CRANpkg{shiny}.

The `as_shared_tsibble()` turns a `tsibble` object to a shared data class, with an option to express any nesting and crossing structures from the `key` attribute. If nesting is found in the data, the `plotly_key_tree()` creates an interactive hierarchical tree to help with data overview. This sets the stage for hierarchical and categorical linking between multiple views from one shared tsibble.

A new shiny module, `tsibbleWrapUI()` and `tsibbleWrapServer()`, provides a lens for looking at temporal aspects of a `tsibble`, in particular seasonal or cyclical variations. The slicing and dicing technique efficiently wrap time lines for user-defined plots. The `plotlyProxy()` react method makes it possible to send wrapped data to the server and amend the plot straight way.

### 2020-09-24 tsibbletalk.tex
done proofing and checking

Close to the heart of the \CRANpkg{tsibbletalk} package is blending the
best bits from \CRANpkg{tsibble}, \CRANpkg{crosstalk}, \CRANpkg{plotly},
and \CRANpkg{shiny}.

The \texttt{as\_shared\_tsibble()} turns a \texttt{tsibble} object to a
shared data class, with an option to express any nesting and crossing
structures from the \texttt{key} attribute. If nesting is found in the
data, the \texttt{plotly\_key\_tree()} creates an interactive
hierarchical tree to help with data overview. This sets the stage for
hierarchical and categorical linking between multi-views from one shared
tsibble.

A new shiny module, \texttt{tsibbleWrapUI()} and
\texttt{tsibbleWrapServer()}, provides a lens for looking at temporal
aspects for a \texttt{tsibble}, in particular seasonal or cyclical
variations. The slicing and dicing technique efficiently wrap time lines
for user-defined plots. The \texttt{plotlyProxy()} react method makes it
possible to send wrapped data to the server and amend the plot straight
way.

>>>>

At the heart of the \CRANpkg{tsibbletalk} package is a blending the best
bits from \CRANpkg{tsibble}, \CRANpkg{crosstalk}, \CRANpkg{plotly}, and
\CRANpkg{shiny}.

The \texttt{as\_shared\_tsibble()} turns a \texttt{tsibble} object to a
shared data class, with an option to express any nesting and crossing
structures from the \texttt{key} attribute. If nesting is found in the
data, the \texttt{plotly\_key\_tree()} creates an interactive
hierarchical tree to help with data overview. This sets the stage for
hierarchical and categorical linking between multiple views from one
shared tsibble.

A new shiny module, \texttt{tsibbleWrapUI()} and
\texttt{tsibbleWrapServer()}, provides a lens for looking at temporal
aspects of a \texttt{tsibble}, in particular seasonal or cyclical
variations. The slicing and dicing technique efficiently wrap time lines
for user-defined plots. The \texttt{plotlyProxy()} react method makes it
possible to send wrapped data to the server and amend the plot straight
way.
